\documentstyle{res} 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\begin{document} 

\name{RAJ KUMAR\\[12pt]}     % the \\[12pt] adds a blank

\vspace{-10pt}

\address{64 W 108 St.\\New York, NY 10025}
\address{(212) 665-4602\\raj@cs.columbia.edu}


\begin{resume}

% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\section{EDUCATION}          
    Columbia University, New York, NY,  Ph.D., Electrical Engineering,
    2008
	\begin{quote} Thesis explored the inherent security of network
    routing protocols and established the theoretic bounds on when
	correctly functioning nodes {\em can and can not} detect
	malfunctioning nodes. Implemented practical algorithms for
	well-known static and dynamic-mobile routing protocols. \\
	Additionally investigated image and video semantics and their use in
	improving video compression. 
	\end{quote} 
	Columbia University, New York, NY,  M.S., Computer Science, 1999
	\begin{quote}
	  Studied use of tertiary-storage in multimedia servers. Extended the
	  relational database model to improve expressability.
\end{quote}
    The Indian Institute of Technology,  Madras, B.Tech. Engineering \\
\vspace{-15pt}
 
\section{EXPERIENCE}
   \vspace{-0.1in}	
%
   \begin{tabbing} \hspace{1.4in}\= \hspace{2.3in}\= \hspace{1.6in}\= \kill 
	 BellCore/Telcordia \>    {\bf Sr. Research Scientist} \>
    2008-Present \>Piscataway, NJ
   \end{tabbing}
   \vspace{-10pt}
   \begin{itemize}
   \item Developed optimal algorithms that allocated wavelengths for a 
   future all-optical core US network made up of optical-switches with
   very limited memory.\\
   \vspace{-15pt}

   \item Modeled Optical Networks (Sonet/Sdh, Dwdm) and implemented automated 
   provisioning of services on these networks. \\
   \vspace{-15pt}

   \item Designed and Implementated Routing and QoS in the IAMANET, a
   intrinsically-secure experimental Internet Architecture. 
   \vspace{-15pt}
   \end{itemize}
%
   \begin{tabbing} \hspace{1.4in}\= \hspace{2.3in}\= \hspace{1.6in}\= \kill 
    Lucent Bell Labs \> {\bf Intern}\>Summer 2006  \>Murray Hill, NJ
   \end{tabbing}
   \vspace{-10pt}
   \begin{itemize}
   \item Developed a library for use by applications to degrade
   gracefully under dynamic denial-of-service (DDOS) attacks and
   overload conditions. The library uses machine-learning techniques
   and feedback from application to selectively discarding requests.
   \end{itemize}
   \vspace{-15pt}
%%
   \begin{tabbing} \hspace{1.4in}\= \hspace{2.3in}\= \hspace{1.6in}\= \kill 
    NEC Labs, America \> {\bf Intern} \>Summer 2005  \>Princeton, NJ
   \end{tabbing}
   \vspace{-10pt}
   \begin{itemize}
   \item Designed an Overlay Network for routing VoIP calls and
   implementeded it on PlanetLab.
   \end{itemize}
   \vspace{-15pt}
%
   \begin{tabbing} \hspace{2.3in}\= \hspace{1.4in}\= \hspace{1.6in}\= \kill 
     Deutsche Bank Proprietary Trading \> {\bf Consultant} \>2001-2004(Part-Time) \>New York, NY
   \end{tabbing}
   \vspace{-10pt}  
   \begin{itemize}
   \item Developed analytic, real-time software for equity pairs-trading and
   convertible bonds. Led effort that oursourced software development
   to India.
   \end{itemize}
   \vspace{-15pt}
%
   \begin{tabbing} \hspace{1.4in}\= \hspace{2.3in}\= \hspace{1.6in}\= \kill 
    Philips Research \> {\bf Intern} \>Summer 2001  \>Scarborough, NY
   \end{tabbing}
   \vspace{-10pt}
   \begin{itemize}
   \item Implemented temporal and spatial scalability in the MPEG-4 codec.
   \end{itemize}
   \vspace{-15pt}
%
   \begin{tabbing} \hspace{1.4in}\= \hspace{2.3in}\= \hspace{1.6in}\= \kill 
    AT\&T Research Labs \> {\bf Consultant} \> 1998-99(Part-Time) \>Red Bank, NJ
   \end{tabbing}
   \vspace{-10pt}
   \begin{itemize}
   \item Implemented image-search features in a virtual shopping environment.
   \end{itemize}
   \vspace{-15pt}
%
   \begin{tabbing} \hspace{1.4in}\= \hspace{2.3in}\= \hspace{1.6in}\= \kill 
    BoxHill Systems \> {\bf Engineer} \> 1994-98(Part-Time) \>New York, NJ
   \end{tabbing}
   \vspace{-10pt}
   \begin{itemize}
     \item Implemented low-level Redundant Arrays of Inexpensive Disk
     system code.
   \end{itemize}

\vspace{-10pt}
\section{HONORS AND AWARDS}          
Elected to Student Senate, The Indian Institute of Technology, Madras \\
Second place, IEEE 2002 Sarnoff Symposium Student Paper Contest 

\vspace{-10pt}
\section{COMPUTER SKILLS}          
    C/C++, Java, PERL, UNIX, Windows, NS2

\section{SELECTED PUBLICATIONS:}
Raj Kumar Rajendran, Vishal Misra, Dan Rubenstein. ``Theoretical
Bounds on Control Plane Self-Monitoring in Routing-Protocols''
{\em ACM Sigmetrics 2007, San Diego, June 2007}\\
   \vspace{-12pt}

Raj Kumar Rajendran, Vishal Misra, Dan Rubenstein. ``Strong
Detection of Misconfigurations'' {\em Brief Announcement, Principles
  of Distributed Computing (PODC)  2005, Las Vegas, July 2005}, {\em
  Full Version, Allerton, Illinois, Sept. 2006}\\
   \vspace{-12pt}

Raj Kumar Rajendran, Dan Rubenstein.``Optimizing the quality of
scalable video streams on P2P Networks'' {\em Extended Abstract in
  ACM Sigmetrics 2004, New York, June 2004}, {\em Full Version in
  Journal of Computing Networks (JCN),  June 2006} \\
   \vspace{-12pt}

Raj Kumar Rajendran, Mihaela van der Scharr, Shih-Fu Chang.``FGS+:
Optimizing the Joint SNR-Temporal Video Quality in MPEG-4 Fine Grained
Scalable Coding'' {\em IEEE International Symposium on Circuits
  and Systems 2002, Phoenix, May 2002} \\
   \vspace{-12pt}

Raj Kumar Rajendran, Shih-Fu Chang.``Image Retrieval with Sketches
and Coherent Images''{\em International Conference on Multimedia
  Exposition 2000, New York, Aug 2000} \\
   \vspace{-12pt}

L. Golubchik, and Raj Kumar Rajendran.``A Study on the use of
Tertiary Storage in Multimedia Systems.''{\em Proceedings of the
  16th IEEE Symposium on Mass Storage Systems, Washington, DC,
  March, 1998.} 

 
\end{resume}
\end{document}
